---
title: "Knowledgeability (02) Analysis"
author: "Matthew Loder"
date: "3/18/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cleaning Scripts:
```{r packages, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(data.table)
library(gridExtra)
library(DescTools)
library(splines)
library(stringr)
library(lme4)
library(knitr)
  
```

## Load in data:
```{r data, echo=FALSE}
d.all = read.csv("exp_data.csv")
```

## Exclusions:

We excluded participants who failed our initial practice question, designed to filter out nonnative speakers of French. 

```{r exclusions, echo=FALSE}
d.practice = read.csv("practice_data.csv")

# Exclude participants that fail the catch question -- In the newest version of the experiment I may add two and only exclude participants that fail both

d.exclusions = d.practice %>%
  filter(condition == "practice1") %>%
  filter(!dsq)

d.all = d.all %>% filter(!(id %in% d.exclusions$id))

print(paste("We excluded", length(d.exclusions$id), "participants on the basis of demonstrated non-native French."))

```

## The results:

Below is a summary of the overall results - 

```{r table1, echo = FALSE}

d.target = d.all %>% filter(type == "target")

percent_dsq = d.target %>% 
  group_by(condition) %>% 
  summarise('percent_in_situ' = mean(dsq),
            'se' = sd(dsq)/sqrt(length(dsq)))

kable(percent_dsq[,1:2], caption='Percent In-Situ by Condition')

```

## Analyze data:

We ran a binomial linear mixed effects model, with subject and wh_word as random effects. We determined these random effects by comparing models containing random effects for item, subject and wh_word.

There does not appear to be anything approaching a significant effect, nor is there a clear qualitative trend in the data.

```{r, echo=FALSE}

model1 = glmer(dsq ~ condition + (1|id) + (1|item) + (1|wh_word), data=d.target, family=binomial)

model2 = glmer(dsq ~ condition + (1|id) + (1|item), data=d.target, family=binomial)

model3 = glmer(dsq ~ condition + (1|item) + (1|wh_word), data=d.target, family=binomial)

model4 = glmer(dsq ~ condition + (1|id) + (1|wh_word), data=d.target, family=binomial)

```

```{r}
summary(model4)
```


## Exploring the data

### Removing the 'quoi' cases

```{r}
d.no_quoi = d.target %>%
  filter(wh_word != "quoi")

model1.2 = glmer(dsq ~ condition + (1|id) + (1|item) + (1|wh_word), data=d.no_quoi, family=binomial)

model2.2 = glmer(dsq ~ condition + (1|id) + (1|item), data=d.no_quoi, family=binomial)

model3.2 = glmer(dsq ~ condition + (1|item) + (1|wh_word), data=d.no_quoi, family=binomial)

model4.2 = glmer(dsq ~ condition + (1|id) + (1|wh_word), data=d.no_quoi, family=binomial)
```

```{r}
summary(model4.2)
```

## Appendix A - Tables

```{r table_whwords, echo=FALSE}
dsq_wh = d.target %>%
  group_by(wh_word, condition) %>%
  summarise('percent_in_situ' = mean(dsq),
            'se' = sd(dsq)/sqrt(length(dsq)))

kable(dsq_wh[, 1:3], caption='Percent In-Situ by WH-Word and Condition')

```

```{r table_items, echo=FALSE}
dsq_items = d.target %>%
  group_by(item, condition) %>%
  summarise('percent_in_situ' = mean(dsq),
            'se' = sd(dsq)/sqrt(length(dsq)))

kable(dsq_items[1:3], caption='Percent In-Situ by Item and Condition')

```

```{r table_subjects}
dsq_subjects = d.target %>%
  group_by(id, condition) %>%
  summarise('percent_in_situ' = mean(dsq),
            'se' = sd(dsq)/sqrt(length(dsq)))

kable(dsq_subjects[1:3], caption='Percent In-Situ by Subject and Condition')
```


## Appendix B - Plots

```{r plot1, echo=FALSE, fig.width=8, fig.height=5}

p1 = ggplot(percent_dsq, aes(x = condition, y = percent_in_situ, fill = condition)) +
    xlab("Condition") +
    ylab("Percent In Situ Responses") +
    geom_col() +
    geom_errorbar(aes(ymin = percent_in_situ - se, ymax = percent_in_situ + se),
                  width = 0.25) +
    guides(col=guide_legend(title="Expr.")) +
    ggtitle("Percent In-Situ for Partial Knowledge and No Knowledge Conditions")

p1
```

```{r plot_wh, echo=FALSE, fig.width=8, fig.height=5}

p2 = ggplot(dsq_wh, aes(x = wh_word, y = percent_in_situ, fill = condition)) +
    xlab("Question Word") +
    ylab("Percent In Situ Responses") +
    geom_col(position=position_dodge()) +
    # geom_errorbar(aes(ymin = percent_in_situ - se, ymax = percent_in_situ + se),
    #             width = 0.25) +
    guides(col=guide_legend(title="Expr.")) +
    ggtitle("Percent In-Situ by WH-Word for Partial Knowledge and No Knowledge Conditions")

p2

```

```{r plot_items, echo=FALSE, fig.width=8, fig.height=5}

p3 = ggplot(dsq_items, aes(x = as.factor(item), y = percent_in_situ, fill = condition)) +
    xlab("Item") +
    ylab("Percent In Situ Responses") +
    geom_col() +
    geom_errorbar(aes(ymin = percent_in_situ - se, ymax = percent_in_situ + se),
                width = 0.25) +
    guides(col=guide_legend(title="Expr.")) +
    ggtitle("Percent In-Situ by Item for Partial Knowledge and No Knowledge Conditions")

p3

```

```{r plot_subjects, echo=FALSE, fig.width=8, fig.height=5}
p4 = ggplot(dsq_subjects, aes(x = as.factor(id), y = percent_in_situ, fill = condition)) +
    xlab("Subject ID") +
    ylab("Percent In Situ Responses") +
    geom_col(position=position_dodge()) +
    # geom_errorbar(aes(ymin = percent_in_situ - se, ymax = percent_in_situ + se),
    #             width = 0.25) +
    guides(col=guide_legend(title="Expr.")) +
    ggtitle("Percent In-Situ by Subject for Partial Knowledge and No Knowledge Conditions")

p4
```

